Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/intro.tex
reworded last few paragraphs to deemphasize the implementation/evaluation

This paper presents an approach to dataflow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object. In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviors will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing dataflow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls.

@@

We implemented the correlated-calls transformation and the IDE algorithm in Scala,
on top of the WALA framework for static analysis of JVM bytecode~\cite{fink2012wala}.
We also report on preliminary experiments in which our correlated-calls transformation
is applied to an IFDS formulation of a simple taint analysis. Our results show that
solving the resulting IDE problem avoids infeasible paths due to correlated calls as
expected.

In summary, the contributions of this paper are as follows:
\begin{itemize}
  \item
    We present a general approach for transforming IFDS problems into corresponding
    IDE problems that avoid infeasible paths due to correlated method calls and
    prove its correctness. 
  \item
    We implemented the approach in Scala, on top of the WALA program analysis framework
    and report on preliminary experiments. 
\end{itemize}

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:ccdatastr} presents the correlated-calls transformation
and sketches a proof of its correctness%
\footnote{
  Detailed proofs of our lemmas and theorems can be found in
  the supplemental materials that are included with this submission.
}.
%
The implementation of our approach and preliminary experiments are discussed
in Section~\ref{chapter:eval}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, conclusions and directions for future work are presented in Section~\ref{sec:Conclusions}.

>>>>

This paper presents an approach to dataflow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object.
%\mtodo{Should we define the term ``receiver''?}
In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviors will be correlated. A recent paper \cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing dataflow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls.

@@

We implemented the correlated-calls transformation and the IDE algorithm in Scala,
on top of the WALA framework for static analysis of JVM bytecode~\cite{fink2012wala}.
Our prototype implementation was tested extensively by using it to transform an IFDS-based 
taint analysis into a more precise IDE-based taint analysis, and applying the latter
to small example programs with correlated calls. Our prototype along with all tests
will be made available to the artifact evaluation committee.

%We also report on preliminary experiments in which our correlated-calls transformation
%is applied to an IFDS formulation of a simple taint analysis. Our results show that
%solving the resulting IDE problem avoids infeasible paths due to correlated calls as
%expected.
%
%In summary, the contributions of this paper are as follows:
%\begin{itemize}
%  \item
%    We present a general approach for transforming IFDS problems into corresponding
%    IDE problems that avoid infeasible paths due to correlated method calls and
%    prove its correctness. 
%  \item
%    We implemented the approach in Scala, on top of the WALA program analysis framework
%    and report on preliminary experiments. 
%\end{itemize}

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:cca} presents the correlated-calls transformation
and sketches a proof of its correctness%
\footnote{
  Detailed proofs of our lemmas and theorems can be found in
  the supplemental materials that are included with this submission.
}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, conclusions and directions for future work are presented in Section~\ref{sec:Conclusions}.
